\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2018-08-07 sections/results.tex
Update Results

  There is significant variation both in the networks as well as the \ac{otu}/\ac{esv} tables when different combinations of methods are used to generate them.
  Figure \ref{fig:otu_correlations} shows the comparison of several denoising and clustering methods.
  The data shows that all the methods that perform either clustering or denoising are highly correlated with each other.
  The correlation is low when comparing a method that performs clustering on the sequences with a method that performs denoising (Figure \ref{fig:otu_correlations}).
  The common core network (network made up of edges that are predicted by all methods) is very small compared to the total number of edges predicted by all the methods (Figure \ref{fig:denoise_network}).
  In this result, only the denoising method was changed (database used: \ac{gg} and network inference: \ac{sparcc}).
  But, nonetheless this approach of identifying a common network will help identify links with a good degree of confidence.

@@

@@

  The pipeline and the data visualization tool help the user explore the effect of the various methods on their data.
  Exploring these differences are difficult and inconvenient without the tool since different tools differ in their input and output formats and require inter-converting between the various formats.
  In the case of our pipeline, this is handled automatically.

  \begin{figure}[h]
    \begin{center}
      \includegraphics[width=17.8cm]{main_figure.png}
      \caption{\textbf{Percentage of variance in the final co-occurrence network due to each processing step.} }
      \label{fig:variance}
    \end{center}
  \end{figure}

  \begin{figure}[h]
    \begin{center}
      \includegraphics[width=15.8cm]{otu_corr_full.pdf}
      \caption{
        \textbf{Comparison of various denoising and clustering algorithms used in the pipeline}.
        (A, B) Correlation of the abundances of the taxa that are common between the count matrices created by two different methods.
        (A) The best correlation (most similar methods) is between open-reference and denovo.
        (B) The worst correlation (least similar methods) is between open-reference and dada2.
        (C) A heatmap showing the $\mathrm{R}^2$ of all pairwise comparisons of the methods.
      }
      \label{fig:otu_correlations}
    \end{center}
  \end{figure}

  \begin{figure}[h]
    \begin{center}
      \includegraphics[width=17.8cm]{tax_comp_full.pdf}
      \caption{\textbf{Taxonomy composition of the 20 most abundant genera predicted using different taxonomy references databases}. NOTE: I will replace the legend with the taxonomy tree}
      \label{fig:tax_comparison}
    \end{center}
  \end{figure}

  \begin{figure}[h]
    \begin{center}
      \includegraphics[width=15.8cm]{tax_distance_deblur.pdf}
      \caption{\textbf{Average percentage of mismatches in taxonomy assignment at various taxonomy levels}. NOTE: I will include a boxplot of the weighted distance in the taxonomy tree}
      \label{fig:tax_mismatches}
    \end{center}
  \end{figure}

  \begin{figure}[h]
    \begin{center}
      \includegraphics[width=17.8cm]{net_inference_comparison.pdf}
      \caption{
        \textbf{Networks generated using different network inference methods}.
        The four different networks generated by different network inference methods are very dissimilar (C).
        (A) The overlaps between the edges among the network5 generated is shown. The number of edges that are common to all networks are very low (5).
        (B) The hamming distance between the networks is shown. The similarity between various methods was found to vary with the data-source used.
      }
      \label{fig:network_comparison}
    \end{center}
  \end{figure}

  \begin{figure}[h]
    \begin{center}
      %\includegraphics[width=17.8cm]{../figures/network_comparison.pdf}
      \caption{\textbf{Core network captures known interactions in vaginal microbiota.} \textbf{a} Core network, obtained by taking the intersection between all the different pipelines. \textbf{b} Vaginal microbiota network as determined by XXX.}
      \label{fig:real_network}
    \end{center}
  \end{figure}

>>>>

We introduce (\hl{insert name here}) a flexible and modular pipeline for 16S data analysis. It incorporates various popular, publicly available tools as well as custom

  \begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{mind_pipeline.pdf}
    \caption{
      \textbf{The workflow of the microbial co-occurrence analysis pipeline}.
      The processes can be grouped into four major steps: \textbf{(A)} denoising and clustering, \textbf{(B)} taxonomy assignment, \textbf{(C)} \ac{otu}/\ac{esv} processing, and \textbf{(D)} network inference.
      Each step incorporates several processes, each of which in turn have several alternate algorithms for the same task (indicated by the text to the right of the blue boxes).
    }
    \label{fig:mind_pipeline}
  \end{figure}

  \FloatBarrier

  \subsection*{Variance among co-occurrence networks}

  Figure \ref{fig:variance} shows the fraction of total variation in the networks as contributed by four different steps in the pipeline.
  \todo[size=\footnotesize]{Results being processed}

  \begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{main_figure.png}
    \caption{\textbf{Percentage of variance in the final co-occurrence network due to each processing step.}}
    \label{fig:variance}
  \end{figure}

  \FloatBarrier

  \subsection*{Denoising and clustering methods are very dissimilar}

  There is significant variation both in the networks as well as the \ac{otu}/\ac{esv} tables when different combinations of methods are used to generate them.
  The \ac{esv} tables generated by methods that perform denoising are very similar to each other and the \ac{otu} tables generated by the clustering methods are very similar to each other, but results of denoising and clustering are highly uncorrelated as shown in Figure \ref{fig:otu_correlations}
  The common core network (network made up of edges that are predicted by all methods) is very small compared to the total number of edges predicted by all the methods (Figure \ref{fig:denoise_network}).
  In this result, only the denoising method was changed (database used: \ac{gg} and network inference: \ac{sparcc}).

  \begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{otu_corr_full.pdf}
    \caption{
      \textbf{Comparison of various denoising and clustering algorithms used in the pipeline}.
      (A, B) Correlation of the abundances of the taxa that are common between the count matrices created by two different methods.
      (A) The best correlation (most similar methods) is between open-reference and denovo.
      (B) The worst correlation (least similar methods) is between open-reference and dada2.
      (C) A heatmap showing the $\mathrm{R}^2$ of all pairwise comparisons of the methods.
    }
    \label{fig:otu_correlations}
  \end{figure}

  \FloatBarrier

  \subsection*{Taxonomy databases vary widely in taxonomy hierarchy and update frequency}

@@

  \begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{tax_comp_full.pdf}
    \caption{\textbf{Taxonomy composition of the 20 most abundant genera predicted using different taxonomy references databases}. NOTE: I will replace the legend with the taxonomy tree}
    \label{fig:tax_comparison}
  \end{figure}

  \begin{figure}[h]
    \centering
    \includegraphics[width=0.95\textwidth]{tax_distance_deblur.pdf}
    \caption{\textbf{Average percentage of mismatches in taxonomy assignment at various taxonomy levels}. NOTE: I will include a boxplot of the weighted distance in the taxonomy tree}
    \label{fig:tax_mismatches}
  \end{figure}

  \subsection*{Network inference contributes to the most variance}

@@

  \begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{net_inference_comparison.pdf}
    \caption{
      \textbf{Networks generated using different network inference methods}.
      The four different networks generated by different network inference methods are very dissimilar (C).
      (A) The overlaps between the edges among the network5 generated is shown. The number of edges that are common to all networks are very low (5).
      (B) The hamming distance between the networks is shown. The similarity between various methods was found to vary with the data-source used.
    }
    \label{fig:network_comparison}
  \end{figure}

  \begin{figure}[h]
    \centering
    %\includegraphics[width=17.8cm]{../figures/network_comparison.pdf}
    \caption{\textbf{Core network captures known interactions in vaginal microbiota.} \textbf{(A)} Core network, obtained by taking the intersection between all the different pipelines. \textbf{(B)} Vaginal microbiota network as determined by XXX.}
    \label{fig:real_network}
  \end{figure}

  % TODO: Based on these results: What is the best pipeline we recommend?
  The pipeline and the data visualization tool help the user explore the effect of the various methods on their data.
  Exploring these differences are difficult and inconvenient without the tool since different tools differ in their input and output formats and require inter-converting between the various formats.
  In the case of our pipeline, this is handled automatically.
